---
title: "Preliminary Analysis Result for OHUN Network"
author: "Amanda(Tianyi) Liu"
date: "16/05/2021"
output:
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/Desktop/CUMC/Practicum/icap-one-health/data/')
```

```{r package, message=FALSE, warning=FALSE}
library(scales)
library(rlist)
library(tidyverse)
library(patchwork)
library(ggplot2)
library(stringr)
library(kableExtra)
```

```{r message=FALSE, warning=FALSE}
f_name <- 'alumni_tracking_05.11_update2.csv'
dat <- read.csv(f_name)
dat <- cbind(id=rownames(dat), dat)
dat <- dat %>% group_by(q7a_ohun_network) %>% rename(OHUN = q7a_ohun_network) 
```

## SECTION 1 - Basic Demographics and One Health Connections

**Q1. Best Way of Communication**
```{r fig.height=5, fig.width=8.5}
q1 <- dat %>% select(starts_with('q1_')) %>%
  summarise_all(funs(count = sum(.=='yes'))) %>%
  rename("Email"=2, "Phone"=3, "MobileApplication"=4, "Other"=5) %>%
  gather(Method, count, -OHUN) %>%
  mutate(Method = factor(Method, unique(Method)))

af <- q1 %>% filter(OHUN=='AFROHUN') %>%
  arrange(desc(Method)) %>%
  mutate(pos = cumsum(count)- count/2, prop = round(100*count/sum(count),2)) %>%
  mutate(prop = paste(prop, "%", sep=''))

sea <- q1 %>% filter(OHUN=='SEAOHUN') %>%
  arrange(desc(Method)) %>%
  mutate(pos = cumsum(count)- count/2, prop = round(100*count/sum(count),2)) %>%
  mutate(prop = paste(prop, "%", sep=''))

colors <- c("#0073C2FF", "#EFC000FF", "#868686FF", "#CD534CFF")

af_plot <- ggplot(af, aes(x="", y=count, fill=Method)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  labs(x='', y='', title="Most Preferred Method Of Communication (Email/Phone/App) - AFROHUN")+
  geom_text(aes(y = pos, label = prop), color = "white") + 
  scale_fill_manual(values = colors) +
  theme_void()

sea_plot <- ggplot(sea, aes(x="", y=count, fill=Method)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  labs(x='', y='', title="Most Preferred Method Of Communication (Email/Phone/App) - SEAOHUN")+
  geom_text(aes(y = pos, label = prop), color = "white") + 
  scale_fill_manual(values = colors) +
  theme_void()

af_plot
sea_plot
```

**Q2. Gender**
```{r fig.height=5, fig.width=8.5}
q2 <- dat %>% select(starts_with('q2_')) %>% rename(Gender=2) %>% count(Gender)

af <- q2 %>% filter(OHUN=='AFROHUN') %>%
  arrange(desc(Gender)) %>%
  mutate(pos = cumsum(n)- n/2, prop = round(100*n/sum(n),2)) %>%
  mutate(prop = paste(prop, "%", sep=''))

sea <- q2 %>% filter(OHUN=='SEAOHUN') %>%
  arrange(desc(Gender)) %>%
  mutate(pos = cumsum(n)- n/2, prop = round(100*n/sum(n),2)) %>%
  mutate(prop = paste(prop, "%", sep=''))

colors <- c("#0073C2FF", "#EFC000FF", "#868686FF", "#CD534CFF")

af_plot <- ggplot(af, aes(x=2, y=n, fill=Gender)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  labs(x='', y='', title="Stratification Based On Gender - AFROHUN")+
  geom_text(aes(y = pos, label = prop), color = "white") + 
  scale_fill_manual(values = colors) +
  theme_void() + theme(plot.title = element_text(hjust = 0.5)) +
  xlim(0.5, 2.5)
  
sea_plot <- ggplot(sea, aes(x=2, y=n, fill=Gender)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  labs(x='', y='', title="Stratification Based On Gender - SEAOHUN")+
  geom_text(aes(y = pos, label = prop), color = "white") + 
  scale_fill_manual(values = colors) +
  theme_void() + theme(plot.title = element_text(hjust = 0.5)) +
  xlim(0.5, 2.5)
  
af_plot
sea_plot
```

**Q3. Age**
```{r fig.height=5, fig.width=8.5}
age_cat = c('17 or younger', 
        '18 to 24', 
        '25 to 29',
        '30 to 34', 
        '35 to 39', 
        '40 to 44', 
        '45 to 49',
        '50 to 54',
        '55 to 59',
        '60 to 64', 
        '65 to 69',
        '70 or older')

q3 <- dat %>% select(id, starts_with('q3_')) %>% rename(Age=3) %>% count(Age)

af <- q3 %>% filter(OHUN=="AFROHUN") %>% 
  full_join(data.frame(age_cat), by = c("Age" = "age_cat")) %>%
  mutate(OHUN="AFROHUN", across(n, ~replace_na(.,0))) %>%
  separate(Age, c("a", NA, NA), sep=' ', remove = FALSE) %>%
  arrange(a) %>% select(-a)

sea <- q3 %>% filter(OHUN=="SEAOHUN") %>% 
  full_join(data.frame(age_cat), by = c("Age" = "age_cat")) %>%
  mutate(OHUN="SEAOHUN", across(n, ~replace_na(.,0))) %>%
  separate(Age, c("a", NA, NA), sep=' ', remove = FALSE) %>%
  arrange(a) %>% select(-a)

af_plot <- ggplot(af, aes(x=age_cat, y=n)) +
  ggtitle("Stratification Of Survey Participants By Age - AFROHUN") + xlab("") + ylab("") +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=n),colour="gray",vjust=-1) +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

sea_plot <- ggplot(af, aes(x=age_cat, y=n)) +
  ggtitle("Stratification Of Survey Participants By Age - SEAOHUN") + xlab("") + ylab("") +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=n),colour="gray",vjust=-1) +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

af_plot
sea_plot
```

**Q7. OHUN Network**
```{r fig.height=5, fig.width=8.5}
q7 <- dat %>% count(OHUN)

participant <- ggplot(q7, aes(x=OHUN, y=n)) +
  ggtitle("Total Number of Participants in Each OHUN") + xlab("") + ylab("") +
  geom_bar(stat="identity", fill="steelblue", width = 0.8) +
  geom_text(aes(label=n),colour="gray",vjust=-1) +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

participant
```

**Q4. Number Of Participants In SEAOHUN And AFROHUN**
```{r fig.height=5, fig.width=8.5}
# uni <- dat %>% select(starts_with('q7_')) %>%
#   summarise_all(funs(count = sum(.=='yes')))
# uni <- uni[order(uni$OHUN),]
#
# names <- lapply(colnames(uni)[-1], function(x) strsplit(x, '_')[[1]]) %>%
#   lapply(function(x) x[length(x)-1]) %>% unlist()
# names <- list.append(c("OHUN"), names)
# colnames(uni) <- names
#
# afr <- uni[1, 11:20] %>% transpose() %>% unlist() %>%
#   data.frame(stringsAsFactors = FALSE) %>%
#   rownames_to_column() %>% `colnames<-`(c('uni', 'n'))
# afr$uni <- factor(afr$uni, levels = unique(afr$uni)[order(afr$n, decreasing = TRUE)])
# afr <- afr[order(afr$n, decreasing = TRUE),] %>% mutate(prop = cumsum(n)/sum(n))
#
# sea <- uni[2, 2:10] %>% transpose() %>% unlist() %>%
#   data.frame(stringsAsFactors = FALSE) %>%
#   rownames_to_column() %>% `colnames<-`(c('uni', 'n'))
# sea$uni <- factor(sea$uni, levels = unique(sea$uni)[order(sea$n, decreasing = TRUE)])
# sea <- sea[order(sea$n, decreasing = TRUE),] %>% mutate(prop = cumsum(n)/sum(n))
# sea
#
# fig1 <- plot_ly(afr)
# fig1 <- fig1 %>% add_trace(x = ~uni, y = ~n, type = 'bar', name = 'Number of Participants',
#             hoverinfo = "text",
#             text = ~n)
# fig1 <- fig1 %>% add_trace(x = ~uni, y = ~prop, type = 'scatter', mode = 'lines', name = 'Cumulative percentage', yaxis = 'y2',
#             line = list(color = '#45171D'),
#             hoverinfo = "text",
#             text = ~prop)
# fig1 <- fig1 %>% layout(title = 'Number of participants enrolled in each AFROHUN',
#          xaxis = list(title = ""),
#          yaxis = list(side = 'left', title = '', zeroline = FALSE),
#          yaxis2 = list(side = 'right', title = '',
#                        overlaying = "y", tickformat = '%', showgrid = FALSE, zeroline = FALSE),
#          showlegend = F,
#          margin = list(r=100))
# fig1
#
# fig2 <- plot_ly(sea)
# fig2 <- fig2 %>% add_trace(x = ~uni, y = ~n, type = 'bar', name = 'Number of Participants',
#             hoverinfo = "text",
#             text = ~n)
# fig2 <- fig2 %>% add_trace(x = ~uni, y = ~prop, type = 'scatter', mode = 'lines', name = 'Cumulative percentage', yaxis = 'y2',
#             line = list(color = '#45171D'),
#             hoverinfo = "text",
#             text = ~prop)
# fig2 <- fig2 %>% layout(title = 'Number of participants enrolled in each SEAOHUN', showlegend = FALSE,
#          xaxis = list(title = ""),
#          yaxis = list(side = 'left', title = '', zeroline = FALSE),
#          yaxis2 = list(side = 'right', title = '',
#                        overlaying = "y", tickformat = '%', showgrid = FALSE, zeroline = FALSE),
#          showlegend = F,
#          margin = list(r=100))
# fig2
```


**Q8. Number Of Participants From Each University In SEAOHUN (Q8) **
```{r fig.height=6, fig.width=11}
q8 <- dat %>% select(starts_with('q8_')) %>% ungroup() %>% summarise_all(funs(count=sum(.=='yes', na.rm = TRUE)))
country_uni <- read.csv('country_uni_list.csv')

plot_chapt <- function(ohun, country_abbr, country){
  uni <- country_uni %>% filter(Country_abbr==country_abbr) %>% select(University) %>% transpose() %>% unlist()
  chapt <- q8 %>% select(contains(country_abbr)) %>% `colnames<-`(uni) %>% transpose() %>% unlist()
  chapt <- data.frame(uni = names(chapt), count = unlist(chapt))
  chapt$uni <- factor(chapt$uni, levels = uni)
  chapt$count <- as.numeric(chapt$count)
  
  ylim <- max(chapt$count)+0.5*max(chapt$count)
  fig <- ggplot(chapt, aes(x=factor(uni,unique(uni)), y=count)) +
    ggtitle(paste("Number Of Participants From Each University In", ohun, '\n', country)) + xlab("") + ylab("") +
    geom_bar(stat="identity", fill="steelblue", width=0.8) +
    geom_text(aes(label=count),colour="gray",hjust=-2)+
    scale_x_discrete(labels = wrap_format(40)) + ylim(0, ylim) +
    theme_minimal() + theme(plot.title = element_text(hjust = 0.5)) +
    coord_flip()

  return(fig)
}

loop <- unique(country_uni[ , 1:3])
for (i in 1:dim(loop)[1]){
  ohun <- loop[i, 1]
  country <- loop[i, 2]
  country_abbr <- loop[i, 3]

  fig <- plot_chapt(ohun, country_abbr, country)
  print(fig)
}
```


**Q9-10. Average Time To Complete OH Training (Q9-10)**
```{r}
q9 <- dat %>% select(id, starts_with(c('q9_', 'q10'))) %>%
  rename(OHUN=1, id=2, start=3, end=4) %>%
  mutate(start = as.numeric(start), end = as.numeric(end), id = as.numeric(id), diff = end - start) %>%
  drop_na()
header <- c("Participant Number", "Year OH Training Began", "Year OH Training Completed/plan to complete", "Difference")

af <- group_split(q9)[[1]] %>% select(-1) %>% relocate(id) %>% `colnames<-`(header)
sea <- group_split(q9)[[2]] %>% select(-1) %>% relocate(id) %>% `colnames<-`(header)
```

```{r}
kable(af, format = "html", caption = "AFROHUN", align = "c") %>% kable_styling()
```
Average number of years to complete OH Training: `r mean(af$Difference)`. 

Minimum number of years to complete OH Training: `r min(af$Difference)`. 

Maximum number of years to complete OH Training: `r max(af$Difference)`. 
 
Median number of years to complete OH Training: `r median(af$Difference)`. 

```{r}
kable(sea, format = "html", caption = "SEAOHUN", align = "c") %>% kable_styling()
```
Average number of years to complete OH Training: `r mean(sea$Difference)`.

Minimum number of years to complete OH Training: `r min(sea$Difference)`.

Maximum number of years to complete OH Training: `r max(sea$Difference)`.

Median number of years to complete OH Training: `r median(sea$Difference)`.


**Trend Analysis of Number of Participants Over Years (Q9-10)**
```{r}
trend <- q9 %>% select(-start, -diff) %>% 
  mutate(dummy="yes") %>% spread(end, dummy) %>% 
  mutate(across(everything(),~replace_na(.x, "no"))) %>%
  gather(Graduation, Status, -OHUN, -id) %>%
  filter(Status=='yes') %>%
  group_by(OHUN, Graduation) %>%
  summarise_at(vars(Status), funs(sum(.=='yes')))

emp <- ggplot(trend, aes(x=factor(Graduation, unique(Graduation)), Status)) + 
  geom_bar(aes(fill = OHUN), position = position_dodge2(preserve = "single", width=0.8), stat = "identity") +
  labs(x='', y='', title="Number of Graduates over Year", subtitle="*based on completion year") +
  scale_fill_manual(values=c("#81b3de", "#f3bc44")) +
  theme_minimal() +  theme(plot.title = element_text(hjust = 0.5), 
                           plot.subtitle = element_text(hjust = 0.5),
                           legend.position="bottom",
                           legend.title = element_blank())
emp
```


**Trend Analysis of Participants’ Gender Over Years (Q2,9,10) **
```{r}
gender <- dat %>% select(id, starts_with('q2_')) %>%
  mutate(id=as.numeric(id), dummy='yes') %>%
  full_join(q9) %>% drop_na() %>%
  select(-start, -diff) %>%
  spread(q2_gender, dummy) %>% mutate(across(everything(),~replace_na(., 'no'))) %>%
  group_by(OHUN, end) %>%
  summarise_at(vars(Female, Male), funs(sum(.=='yes'))) %>%
  gather(Gender, Count, -OHUN, -end)
gender

af <- ggplot(filter(gender, OHUN=="AFROHUN"), aes(x=factor(end, unique(end)), Count)) + 
  geom_bar(aes(fill = Gender), position = position_dodge2(preserve = "single", width=0.8), stat = "identity") +
  labs(x='', y='', title="Graduate Genders Throughout Years - AFROHUN", subtitle="*based on completion year") +
  scale_fill_manual(values=c("#81b3de", "#8fc056")) +
  theme_minimal() +  theme(plot.title = element_text(hjust = 0.5), 
                           plot.subtitle = element_text(hjust = 0.5),
                           legend.position="bottom",
                           legend.title = element_blank())

sea <- ggplot(filter(gender, OHUN=="SEAOHUN"), aes(x=factor(end, unique(end)), Count)) + 
  geom_bar(aes(fill = Gender), position = position_dodge2(preserve = "single", width=0.8), stat = "identity") +
  labs(x='', y='', title="Graduate Genders Throughout Years - SEAOHUN", subtitle="*based on completion year") +
  scale_fill_manual(values=c("#81b3de", "#8fc056")) +
  theme_minimal() +  theme(plot.title = element_text(hjust = 0.5), 
                           plot.subtitle = element_text(hjust = 0.5),
                           legend.position="bottom",
                           legend.title = element_blank())

af
sea
```


**Q11. The Most Common Route Of Association Between The Participants And The OHUN (Q11)**
```{r}
q11 <- dat %>% select(starts_with('q11_'), -contains("other"))
row_label <- c("In-service, (training taken during employment)",
               "Pre-service (trained before employment)",
               "Student club member, only")
col_label <- c("Completed a few hours of training (but not a curriculum or program; did not formally graduate)",
               "Completed a single formal curriculum or program of study (and have have graduated)",
               "Completed multiple programs of study (and have graduated)")


```


**Q12. Bar Graph Of The Total Degrees Obtained (Q12)**
```{r fig.height=5, fig.width=8.5}
q12 <- dat %>% select(id, starts_with(c('q12_', 'q10'))) %>%
  rename("Bachelor's Degree (BA, BS, BSc)" = 3, 
         "Master's Degree (MSc, MA, MSPH, MBA)" = 4,
         "Doctoral (academic) Degree (PhD, ScD, EdD)" = 5,
         "Professional Degree (JD, MD)" = 6,
         "Other" = 7,
         "Spec" = 8,
         "Completion" = 9) %>%
  spread(Other, Spec) %>% select(-no) %>%
  mutate(Other = ifelse(is.na(yes), 'no', 'yes'), across(everything(), ~replace_na(.x, "REMOVE"))) %>%
  mutate(yes = paste("Other:", yes)) %>%
  spread(yes, Other) %>% select(-"Other: REMOVE") %>% 
  mutate(across(everything(), ~replace_na(.x, "no")))

q12_p1 <- q12 %>% summarise_all(funs(sum(.=="yes"))) %>%
  gather(Degree, Num, -OHUN, -id)

af <- ggplot(filter(q12_p1, OHUN=='AFROHUN'), aes(x=factor(Degree,unique(Degree)), y=Num)) +
  ggtitle("Bar Graph Of The Total Degrees Obtained (Q12) - AFROHUN") + xlab("") + ylab("") +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=Num),colour="gray",vjust=-1) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

sea <- ggplot(filter(q12_p1, OHUN=='SEAOHUN'), aes(x=factor(Degree,unique(Degree)), y=Num)) +
  ggtitle("Bar Graph Of The Total Degrees Obtained (Q12) - SEAOHUN") + xlab("") + ylab("") +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=Num),colour="gray",vjust=-1) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

af
sea
```
```{r}
q12_p2 <- q12 %>% mutate(Completion = as.numeric(Completion)) %>% drop_na(Completion) %>%
  group_by(OHUN, Completion) %>%
  summarise_all(funs(sum(.=='yes'))) %>%
  gather("Degree", "Num", -OHUN, -id, -Completion) %>%
  mutate(Completion=as.character(Completion), Degree=factor(Degree,unique(Degree))) %>%
  filter_at(vars(Num), any_vars(.!=0))

af <- group_split(q12_p2)[[1]]
sea <- group_split(q12_p2)[[2]]

af_legend <- ceiling(length(unique(af$Degree)) / 3)
sea_legend <- ceiling(length(unique(sea$Degree)) / 3)

af_plot <- ggplot(af, aes(x = Completion, y = Num, fill = Degree, label = Num)) +
  geom_bar(stat = "identity")+
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  ggtitle("Number of Degrees Per Completion Year - AFROHUN") + xlab("") + ylab("")+
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +
  guides(fill=guide_legend(nrow=af_legend,byrow=TRUE))

sea_plot <- ggplot(sea, aes(x = Completion, y = Num, fill = Degree, label = Num)) +
  geom_bar(stat = "identity")+
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  ggtitle("Number of Degrees Per Completion Year - SEAOHUN") + xlab("") + ylab("")+
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom")+
  guides(fill=guide_legend(nrow=sea_legend,byrow=TRUE))

af_plot
sea_plot
```


**Q13-14. Bar Graph Representing Employment Status Pre And Post OH Training: (Q13-14)**
```{r fig.height=6, fig.width=11}
type <- c("Employed full time (40h)",
          "Employed part time (< 40 hours)",
          "Undergraduate student full time",
          "Undergraduate student part time",
          "Graduate/professional school full time",
          "Graduate/professional school part time",
          "Seeking employment",
          "Seeking more education",
          "Volunteer, retired, taking a leave of absence (due to maternity leave, for example)",
          "Other")

q13 <- dat %>% select(starts_with('q13_'), -contains("spec")) %>%
  `colnames<-`(c('OHUN', type)) %>% 
  mutate(across(everything(), ~replace_na(.x, "no"))) %>%
  summarise_all(funs(sum(.=='yes'))) %>%
  gather(Employment, Count, -OHUN) %>%
  mutate(Time = 'Prior to OH Traning')

q14 <- dat %>% select(starts_with('q14_'), -contains("spec")) %>%
  `colnames<-`(c('OHUN', type)) %>% 
  mutate(across(everything(), ~replace_na(.x, "no"))) %>%
  summarise_all(funs(sum(.=='yes'))) %>%
  gather(Employment, Count, -OHUN) %>%
  mutate(Time = 'Post OH Traning')

concat <- rbind(q13, q14)
concat$Time <- factor(concat$Time , levels = unique(concat$Time))

af <- ggplot(filter(concat, OHUN=="AFROHUN"), aes(Employment, Count)) + 
  geom_bar(aes(fill = Time, color = Time), position = "dodge", stat = "identity") +
  ggtitle("Employment Status Prior And Post Oh Training - AFROHUN") + xlab("") + ylab("") +
  scale_x_discrete(labels = wrap_format(30), limits=rev) + 
  theme_minimal() +  theme(plot.title = element_text(hjust = 0.5), 
                           legend.position="bottom",
                           legend.title = element_blank()) + 
  coord_flip()

sea <- ggplot(filter(concat, OHUN=="SEAOHUN"), aes(Employment, Count)) +  
  geom_bar(aes(fill = Time, color = Time), position = "dodge", stat = "identity") +
  ggtitle("Employment Status Prior And Post Oh Training - SEAOHUN") + xlab("") + ylab("") +
  scale_x_discrete(labels = wrap_format(30), limit=rev) + 
  theme_minimal() +  theme(plot.title = element_text(hjust = 0.5), 
                           legend.position="bottom",
                           legend.title = element_blank()) +
  coord_flip()

af
sea
```


**Q15. Table representing Current Alumni Employment Status (Q15)**
```{r}
q15 <- dat %>% select(id, starts_with(c('q15', 'q4'))) %>% drop_na() %>%
  rename("Participant Number" = 2,
         "Employer Name/Name of Company" = 3,
         "Full Job Title" = 4,
         "Country" = 5,
         "City" = 6,
         "Country of Origin" = 7) %>%
  unite("Country & City Where Respondent Works", c(Country, City), sep = ", ") %>%
  select(-5:6)

q15 <- q15[c(2, 1, 5, 6, 3, 4)]
kable(filter(q15, OHUN=="AFROHUN"), format = "html", caption = "AFROHUN", align = "c") %>% kable_styling()
kable(filter(q15, OHUN=="SEAOHUN"), format = "html", caption = "SEAOHUN", align = "c") %>% kable_styling()
```


## SECTION 2 - OHUN PARTICIPATION DETAILS


**Q16-17. Bar Graph Showing The Top Favorite and Least Favorite Courses (Q17-18)**
```{r}
course_list <- c("Behavior Change",
                 "Collaboration and Partnerships",
                 "Communications and Informatics",
                 "Culture, Beliefs, Values and Ethics",
                 "Ecosystem Health",
                 "Epidemiology and Risk Analysis",
                 "Fundamentals of Infectious Disease",
                 "Infectious Disease Management",
                 "Leadership",
                 "Management",
                 "One Health Concepts and Knowledge",
                 "Policy, Advocacy and Regulation",
                 "Public Health",
                 "Systems Thinking")

fav <- dat %>% select(starts_with("q16")) %>%
  mutate(across(everything(), ~replace_na(.x, "no")))
fav_s <- fav %>% select(contains("seaohun"))
fav_a <- fav %>% select(contains("afrohun"))
fav_s
fav_a
# lfav <-
```