---
title: "Preliminary Analysis"
author: "Amanda(Tianyi) Liu"
date: "16/05/2021"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/Desktop/CUMC/Practicum/icap-one-health/data/')
library(scales)
library(rlist)
library(tidyverse)
library(plotly)
library(patchwork)
library(knitr)
library(kableExtra)
```

```{r}
f_name <- 'alumni_tracking_05.11_update2.csv'
dat <- read.csv(f_name, row.names = NULL) 
dat <- dat %>% group_by(q7a_ohun_network) %>% rename(OHUN = q7a_ohun_network)
# head(dat)
```

**Q1. Best Way of Communication**
```{r}
q1 <- dat %>% select(starts_with('q1_')) %>%
  summarise_all(funs(count = sum(.=='yes'))) %>%
  rename(Email=2, Phone=3,MobileApplication=4, Other=5) %>%
  gather(variable, value, -OHUN)

fig <- plot_ly()
fig <- fig %>% add_pie(data=filter(q1, OHUN=='SEAOHUN'), labels = ~variable, values = ~value, name = 'SEAOHUN',
                       textposition = 'inside',textinfo = 'label+percent',insidetextorientation='radial',
                       domain = list(row = 0, column = 0)) 
fig <- fig %>% add_pie(data=filter(q1, OHUN=='AFROHUN'), labels = ~variable, values = ~value, name = 'AFROHUN',
                       textposition = 'inside',textinfo = 'label+percent', insidetextorientation='radial',
                       domain = list(row = 0, column = 1))

fig <- fig %>% layout(title = "Most Preferred Method Of Communication (Email/Phone/App)", showlegend = F,
                      grid=list(rows=1, columns=2),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE)) %>% 
  add_annotations(x=seq(0.2,0.2 + 1*0.5,0.5),
                y=0,
                text = c("SEAOHUN", "AFROHUN"),
                xref = "paper",
                yref = "paper",
                xanchor = "left",
                showarrow = FALSE)

fig
```

**Q2. Gender**
```{r}
q2 <- dat %>% select(starts_with('q2_')) %>% rename(gender=2) %>% count(gender)

fig <- plot_ly()
fig <- fig %>% add_pie(data = filter(q2, OHUN=='SEAOHUN'), labels = ~gender, values = ~n, hole = 0.6, name = 'SEAOHUN',
                       textposition = 'inside',textinfo = 'label+percent',insidetextorientation='radial',
                       domain = list(row = 0, column = 0)) 
fig <- fig %>% add_pie(data = filter(q2, OHUN=='AFROHUN'), labels = ~gender, values = ~n, hole = 0.6, name = 'AFROHUN',
                       textposition = 'inside',textinfo = 'label+percent',insidetextorientation='radial',
                       domain = list(row = 0, column = 1))

fig <- fig %>% layout(title = "Stratification Based On Gender", showlegend = F,
                      grid=list(rows=1, columns=2),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE)) %>% 
  add_annotations(x=seq(0.2,0.2 + 1*0.5,0.5),
                y=0,
                text = c("SEAOHUN", "AFROHUN"),
                xref = "paper",
                yref = "paper",
                xanchor = "left",
                showarrow = FALSE)

fig
```

**Q3. Age**
```{r}
q3 <- dat %>% select(starts_with('q3_')) %>% rename(age=2) %>% count(age)

age = c('17 or younger', '18 to 24', '25 to 29','30 to 34', '35 to 39', '40 to 44', '45 to 49','50 to 54',
          '55 to 59','60 to 64', '65 to 69','70 or older')
q3_options <- data.frame(OHUN = c(rep('SEAOHUN', length(age)), rep('AFROHUN', length(age))),
                         age = rep(age, 2),
                         count = rep(0, 2*length(age)))

q3_full <- left_join(q3_options, q3) %>% mutate_if(is.numeric,coalesce,0) %>% mutate(n = count + n)

# plot annotation
sea <- list(
  text = "SEAOHUN",
  xref = "paper",
  yref = "paper",
  yanchor = "top",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

afr <- list(
  text = "AFROHUN",
  xref = "paper",
  yref = "paper",
  yanchor = "top",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

fig1 <- plot_ly(data = filter(q3_full, OHUN=='SEAOHUN'), x = ~age, y = ~n, 
                 name = "SEAOHUN", type = "bar") %>% 
  add_text(text=~n, hoverinfo='none', textposition = 'top', showlegend = FALSE,
           textfont=list(size=10, color="grey")) %>%
  layout(annotations = sea)

fig2 <- plot_ly(data = filter(q3_full, OHUN=='AFROHUN'), x = ~age, y = ~n, 
                 name = "AFROHUN", type = "bar") %>% 
  add_text(text=~n, hoverinfo='none', textposition = 'top', showlegend = FALSE,
           textfont=list(size=10, color="grey")) %>%
  layout(annotations = afr)

fig <- subplot(fig1, fig2) %>% layout(title="Stratification Based on Age", showlegend = FALSE)
fig
```

**Q7. OHUN Network**
```{r}
q7 <- dat %>% count(OHUN) %>% rename(count = n)
fig <- plot_ly(data = q7, x = ~OHUN, y = ~count, type = "bar", name = "participants") %>%
  layout(title = "Total Number of Participants in Both OHUN") %>%
  add_text(text=~count, hoverinfo='none', textposition = 'top', showlegend = FALSE,
           textfont=list(size=10, color="grey"))

fig
```

**Q4. Number Of Participants In SEAOHUN And AFROHUN**
```{r}
uni <- dat %>% select(starts_with('q7_')) %>%
  summarise_all(funs(count = sum(.=='yes')))
uni <- uni[order(uni$OHUN),]

names <- lapply(colnames(uni)[-1], function(x) strsplit(x, '_')[[1]]) %>%
  lapply(function(x) x[length(x)-1]) %>% unlist()
names <- list.append(c("OHUN"), names)
colnames(uni) <- names

afr <- uni[1, 11:20] %>% transpose() %>% unlist() %>% 
  data.frame(stringsAsFactors = FALSE) %>% 
  rownames_to_column() %>% `colnames<-`(c('uni', 'n'))
afr$uni <- factor(afr$uni, levels = unique(afr$uni)[order(afr$n, decreasing = TRUE)]) 
afr <- afr[order(afr$n, decreasing = TRUE),] %>% mutate(prop = cumsum(n)/sum(n))

sea <- uni[2, 2:10] %>% transpose() %>% unlist() %>%
  data.frame(stringsAsFactors = FALSE) %>% 
  rownames_to_column() %>% `colnames<-`(c('uni', 'n'))
sea$uni <- factor(sea$uni, levels = unique(sea$uni)[order(sea$n, decreasing = TRUE)]) 
sea <- sea[order(sea$n, decreasing = TRUE),] %>% mutate(prop = cumsum(n)/sum(n))
sea

fig1 <- plot_ly(afr)
fig1 <- fig1 %>% add_trace(x = ~uni, y = ~n, type = 'bar', name = 'Number of Participants',
            hoverinfo = "text",
            text = ~n)
fig1 <- fig1 %>% add_trace(x = ~uni, y = ~prop, type = 'scatter', mode = 'lines', name = 'Cumulative percentage', yaxis = 'y2',
            line = list(color = '#45171D'),
            hoverinfo = "text",
            text = ~prop)
fig1 <- fig1 %>% layout(title = 'Number of participants enrolled in each AFROHUN',
         xaxis = list(title = ""),
         yaxis = list(side = 'left', title = '', showgrid = FALSE, zeroline = FALSE),
         yaxis2 = list(side = 'right', title = '', 
                       overlaying = "y", tickformat = '%', showgrid = FALSE, zeroline = FALSE),
         showlegend = F,
         margin = list(r=100))
fig1

fig2 <- plot_ly(sea)
fig2 <- fig2 %>% add_trace(x = ~uni, y = ~n, type = 'bar', name = 'Number of Participants',
            hoverinfo = "text",
            text = ~n)
fig2 <- fig2 %>% add_trace(x = ~uni, y = ~prop, type = 'scatter', mode = 'lines', name = 'Cumulative percentage', yaxis = 'y2',
            line = list(color = '#45171D'),
            hoverinfo = "text",
            text = ~prop)
fig2 <- fig2 %>% layout(title = 'Number of participants enrolled in each SEAOHUN', showlegend = FALSE,
         xaxis = list(title = ""),
         yaxis = list(side = 'left', title = '', showgrid = FALSE, zeroline = FALSE),
         yaxis2 = list(side = 'right', title = '',
                       overlaying = "y", tickformat = '%', showgrid = FALSE, zeroline = FALSE),
         showlegend = F,
         margin = list(r=100))
fig2
```

**Q8. Number Of Participants From Each University In SEAOHUN-THOHUN (Q8) **
```{r}
q8 <- dat %>% select(starts_with('q8_')) %>% ungroup() %>% summarise_all(funs(count=sum(.=='yes', na.rm = TRUE)))
country_uni <- read.csv('country_uni_list.csv')

plot_sea <- function(ohun, country){
  uni <- country_uni %>% filter(Country==country) %>% select(University) %>% transpose() %>% unlist()
  chapt <- q8 %>% select(contains(country)) %>% `colnames<-`(uni) %>% transpose() %>% unlist()
  chapt <- data.frame(uni = names(chapt), count = unlist(chapt))
  chapt$uni <- factor(chapt$uni, levels = uni)
  
  fig <- plot_ly(chapt, x=~uni, y=~count, type='bar') %>% 
  layout(title = paste("Number Of Participants From Each University In", ohun, '-', country),
         xaxis = list(title = ""),
         yaxis = list(side = 'left', title = ''),
         margin = list(l=20, r=20, b=250),
         showlegend = F)
  # %>% add_text(text=~count, hoverinfo='none', textposition = 'top', showlegend = FALSE,
  #          textfont=list(size=10, color="grey"))
  
  fig
}

plot_af <- function(ohun, country_abr, country){
  uni <- country_uni %>% filter(Country==country) %>% select(University) %>% transpose() %>% unlist()
  chapt <- q8 %>% select(contains(country_abr)) %>% `colnames<-`(uni) %>% transpose() %>% unlist()
  chapt <- data.frame(uni = names(chapt), count = unlist(chapt))
  chapt$uni <- factor(chapt$uni, levels = uni)
  
  fig <- plot_ly(chapt, x=~uni, y=~count, type='bar') %>% 
  layout(title = paste("Number Of Participants From Each University In", ohun, '-', country),
         xaxis = list(title = "", tickmode = 'array', ticktext = uni, tickvalue = c(1:length(uni))),
         yaxis = list(side = 'left', title = ''),
         margin = list(l=50, r=50, t=50, b=300),
         showlegend = F) 
  # %>% add_text(text=~count, hoverinfo='none', textposition = 'top', showlegend = FALSE,
  #          textfont=list(size=10, color="grey"))
  fig
}

plot_sea('SEAOHUN', 'CAMBOHUN')
plot_sea('SEAOHUN', 'INDOHUN')
plot_sea('SEAOHUN', 'LAOHUN')
plot_sea('SEAOHUN', 'MMOHUN')
plot_sea('SEAOHUN', 'MyOHUN')
plot_sea('SEAOHUN', 'PhilOHUN')
plot_sea('SEAOHUN', 'THOHUN')
plot_sea('SEAOHUN', 'VOHUN')
plot_af('AFOHUN', 'cameroon', 'CAMEROON')
plot_af('AFOHUN', 'cote_divoire', 'CÔTE D’IVOIRE')
plot_af('AFOHUN', 'drc', 'DEMOCRATIC REPUBLIC OF THE CONGO')
plot_af('AFOHUN', 'ethiopia', 'ETHIOPIA')
plot_af('AFOHUN', 'kenya', 'KENYA')
plot_af('AFOHUN', 'senegal', 'SENEGAL')
plot_af('AFOHUN', 'tanzania', 'TANZANIA')
plot_af('AFOHUN', 'rwanda', 'RWANDA')
plot_af('AFOHUN', 'uganda', 'UGANDA')
```

**Average Time To Complete OH Training (Q9-10)**
```{r}
q9 <- dat %>% select(starts_with(c('q9_', 'q10'))) %>% 
  `colnames<-`(c("OHUN", "start", "end")) %>% 
  filter(grepl("^[0-9]", start)) %>%
  mutate(start = as.numeric(start), end = as.numeric(end), id = row_number(), diff = end-start)

header <- c("Participant Number", "Year OH Training Began", "Year OH Training Completed/plan to complete", "Difference")

af <- group_split(q9)[[1]] %>% select(-1) %>% relocate(id) %>% `colnames<-`(header)
sea <- group_split(q9)[[2]] %>% select(-1) %>% relocate(id) %>% `colnames<-`(header)
```

```{r}
kable(af, format = "html", caption = "AFROHUN", align = "c") %>% kable_styling()
```
Average number of years to complete OH Training: `r mean(af$Difference)`. 

Minimum number of years to complete OH Training: `r min(af$Difference)`. 

Maximum number of years to complete OH Training: `r max(af$Difference)`. 

Median number of years to complete OH Training: `r median(af$Difference)`. 

```{r}
kable(sea, format = "html", caption = "SEAOHUN", align = "c") %>% kable_styling()
```
Average number of years to complete OH Training: `r mean(sea$Difference)`. 

Minimum number of years to complete OH Training: `r min(sea$Difference)`. 

Maximum number of years to complete OH Training: `r max(sea$Difference)`. 

Median number of years to complete OH Training: `r median(sea$Difference)`. 

